---
title: "An Unusual Ransom"
output: html_document
---

## SPOILERS BELOW!!! ##

```{r setup, echo = FALSE}
knitr::opts_chunk$set(warning = FALSE, cache = TRUE, message = FALSE, fig.width = 10, fig.height = 9)
```

```{r, package-import}
library(ggplot2)
library(readr)
library(dplyr)
library(gridExtra)
library(GGally)
library(gganimate)
```

```{r, first-section-data}
part1 = read_csv("https://raw.githubusercontent.com/hyperc54/data-puzzles-assets/master/visualisation/chal1/chal_visu_1_q1_data.csv")
```

The given data are 2-dimensional points with labels x and y. There appeared to be a lot of overplotting near (0, 0), so I zoomed in there, uncovering the word "leafy." This was the first answer.

```{r, visualization-1}
part1 %>% ggplot(aes(x, y)) + geom_point(alpha = 0.1) + theme_bw() + ggtitle("Visualization With Transparency")
part1 %>% filter(0 < x, x < 1500, -300 < y, y < 0) %>% ggplot(aes(x, y)) + geom_point() + theme_bw() + ggtitle("Visualization of Central Points")
```

```{r, second-section-data}
part2 = read_csv("https://raw.githubusercontent.com/hyperc54/data-puzzles-assets/master/visualisation/chal1/chal_visu_1_q2_data.csv")
```

The second data set has seven features, labeled 0 through 6. I ran pairwise correlations and plotted the resulting 2d plots, discovering a prancing unicorn. "unicorn" was the second answer.

```{r, visualization-2}
ggpairs(part2)
```

```{r, third-section-data}
part3 = read_csv("https://raw.githubusercontent.com/hyperc54/data-puzzles-assets/master/visualisation/chal1/chal_visu_1_q3_data.csv")
```

The third data set contains numbers labeled x and y as well as a third "mystery feature." I visualized the x and y coordinates spatially as in part 1 and colored the points according to their "mystery value" but this did not reveal anything obvious. I thought about combining two or more coordinates and tried to look for pairwise correlations in the combined values.

```{r, third-section-visualization}
part3 %>% ggplot(aes(x = x, y = y, color = mystery_feature)) + geom_point()
part3 = part3 %>% mutate(x_plus = x + mystery_feature, x_minus = x - mystery_feature, y_plus = y + mystery_feature, y_minus = y - mystery_feature)
ggpairs(part3)
part3 %>% ggplot(aes(mystery_feature, y + mystery_feature)) + geom_point()
```

Then I thought about treating the mystery_feature value as a frame and viewing the x-y coordinates as an animation. Doing this created a stream of what looked like letters; slowing it down revealed the message containing the final message: "THE ANSWER IS CRUSH".

```{r, animation}
anim = part3 %>% ggplot(aes(x, y)) + geom_point() + transition_time(mystery_feature)
animate(anim)
```

Using the three words together maps you to the final answer!