---
title: "Treasure Hunt"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, fig.height = 6, fig.width = 10, cache = T)
library(readr)
library(tidyverse)
library(cppRouting)
```

## Part 1

```{r data}
temps <- read_delim("https://www.data.gouv.fr/en/datasets/r/882ceb4e-976d-48f7-867a-3efe307c0af3", 
                    ";", escape_double = FALSE, col_names = FALSE, 
                    comment = "#", trim_ws = TRUE) %>% select(1:7)
names(temps) = c("Point", "Lat", "Long", "Context", "Avg", "Month", "Temp")
```

Having downloaded monthly average temperatures for locations in France I will rank them by how closely they match the specified annual temperature profile. A closely-matching point near a city with population 45K is probably the answer.

```{r temp_month}
temps_wide = temps %>% group_by(Point, Avg, Lat, Long) %>% summarise("M1" = sum(Temp * (Month == 1)),
                                                                     "M2" = sum(Temp * (Month == 2)),
                                                                     "M3" = sum(Temp * (Month == 3)),
                                                                     "M4" = sum(Temp * (Month == 4)),
                                                                     "M5" = sum(Temp * (Month == 5)),
                                                                     "M6" = sum(Temp * (Month == 6)),
                                                                     "M7" = sum(Temp * (Month == 7)),
                                                                     "M8" = sum(Temp * (Month == 8)),
                                                                     "M9" = sum(Temp * (Month == 9)),
                                                                     "M10" = sum(Temp * (Month == 10)),
                                                                     "M11" = sum(Temp * (Month == 11)),
                                                                     "M12" = sum(Temp * (Month == 12))) %>%
  mutate(SqDiff = (M1-5.6)^2 + (M2-5.9)^2 + (M3-8.1)^2 + (M4-10.2)^2 + (M5-13)^2 + (M6-15.7)^2 + (M7-17.4)^2 + (M8-17.4)^2 + (M9-15.9)^2 + (M10-12.5)^2 + (M11-8.7)^2 + (M12-6.5)^2) %>% arrange(SqDiff)
temps_wide %>% ggplot(aes(x=Long, y=Lat, z = -SqDiff)) + stat_summary_hex(bins = 100) + scale_fill_viridis_c(option="magma")
```

The map above shows the negative squared difference between locations' monthly average temperature and the provided profile. The northern coast seems to match the temperature profile the best. I was able to find the city with just a few guesses.

## Part 2

```{r graph-setup}
edges = read_csv("https://raw.githubusercontent.com/hyperc54/data-puzzles-assets/master/misc/treasure/graph_data_st_malo.csv")
names(edges) = c("From", "To", "Cost", "Label")
graph = makegraph(edges[,-4], directed = F)
```

```{r Dijkstra}
path = get_multi_paths(graph, "START", "END")[[1]][[1]]
```

```{r Names}
ans = ""
for(i in 1:(length(path) - 1)){
  lbl = edges %>% filter((From == path[i] & To == path[i+1]) | 
                     (From == path[i+1] & To == path[i])) %>% select("Label")
  ans = paste0(substring(lbl[[1]][1], 1, 1), ans)
}
ans
```

## Part 3

```{r marbles-data}
marbles = read_csv("https://raw.githubusercontent.com/hyperc54/data-puzzles-assets/master/misc/treasure/marbles_quizz.csv")
ggplot(data = marbles, aes(x = weight, fill = color)) + geom_density(alpha = 0.3)
```

The one weight variable doesn't seem to neatly split the weights, but the values seem to have a 3-digit integer component and a 3-digit decimal component. I will split these and then try looking for patterns in color.

```{r splitting-number}
marbles = marbles %>% mutate(integer_part = floor(weight),
                             decimal_part = (weight - floor(weight)) * 1000)

ggplot(marbles, aes(x = integer_part, y = decimal_part, color = color)) + geom_point()
```

This is an easy linear split along y=x.

```{r}
marbles_test = marbles %>% filter(color == "?")
nrow(marbles_test %>% filter(integer_part > decimal_part))
```

