---
title: "Follow The Snake"
output: html_document
---

## SPOILERS BELOW!!! ##

```{r setup, echo = FALSE}
knitr::opts_chunk$set(warning = FALSE, cache = TRUE, message = FALSE)
```

```{r, package-import}
library(ggplot2)
library(RNiftyReg)
library(magick)
library(gganimate)
```

I first load the data set and label four snake images N, S, E, and W as indicated on the puzzle page.

```{r, load-data}
snakes = lapply(list.files("data-puzzles-assets-master/computervision/snakes"),
                function(x){image_read(paste0("data-puzzles-assets-master/computervision/snakes/", x)) %>% image_quantize(colorspace = 'gray')})
north = snakes[[2]]
south = snakes[[18]]
east = snakes[[1]]
west = snakes[[14]]
```

For each image, I find which of the labeled snake images it is most similar to (using an image similarity function). The most similar image is used as a label.

```{r, image-similarity}
label_image = function(image){
  sim_n = image_compare_dist(north, image)[[1]]
  sim_s = image_compare_dist(south, image)[[1]]
  sim_e = image_compare_dist(east, image)[[1]]
  sim_w = image_compare_dist(west, image)[[1]]
  sims = c(sim_n, sim_s, sim_e, sim_w)
  label = c("N", "S", "E", "W")[which(sims == max(sims))]
}
snake_labels = unlist(lapply(snakes, label_image))
```

I start a path at the origin and follow the direction of each snake, spelling out the snake's name, "Cascabel" (with a few extra S's of course.)

```{r, figuring-out-what-labels-mean}
x_coord = 0
y_coord = 0
path_points = data.frame(t = 0, x = x_coord, y = y_coord)
for(i in 1:length(snake_labels)){
  label = snake_labels[i]
  y_coord = ifelse(label == "N", y_coord + 1, ifelse(label == "S", y_coord - 1, y_coord))
  x_coord = ifelse(label == "E", x_coord + 1, ifelse(label == "W", x_coord - 1, x_coord))
  path_points[i+1,] = c(i, x_coord, y_coord)
}
path_points %>% ggplot(aes(x, y)) + geom_path()
```

